\subsection{\ifenglish Upload Directory Resolution On Azure Blob Storage\else การระบุไดเรกทอรีสำหรับการอัปโหลดบน Azure Blob Storage\fi}

The Tusd server provides a hook system that triggers user-defined actions in response to specific events, such as when an upload is initiated or completed. This system supports various use cases, including logging, validation, authorization, and post-processing of uploaded files.

One key feature of the Tusd hook system is that the server awaits a response from the service receiving the hook. This is particularly useful for our needs, as we require the Tusd server to receive a response from the processing service before proceeding.

By default, Tusd servers store all uploaded files in a single directory, which does not align with our requirement to organize uploads based on individual users and their respective organizations. To address this, we developed a custom hook that dynamically assigns upload directories according to the user's ID and organization ID.

In our implementation, clients initiate an upload resource without specifying the target directory, ensuring they cannot influence the file path on Azure Blob Storage. Instead, users are required to provide a token during session creation to prevent them from encoding malicious information. Since the Tusd server lacks the secret key to decode user tokens, our custom hook communicates with the backend service to decode the token, retrieving the necessary user and organization identifiers.

\insertPDFfigure
{resources/tusd/tusd-upload-process.pdf}
{\ifenglish File Upload Sequence of Tusd Service\else ขั้นนตอนการอัปโหลดไฟล์ของ Tusd\fi}
{tusd upload progress}

Traditionally, the Tusd hook system operates by sending event notifications to an external service specified by the developer. This external service then processes the events accordingly. In contrast, our implementation integrates event message handling directly within the Tusd server, eliminating the need for a separate service and simplifying the architecture.